---
title: 'Analyses for: Dimensions of adversity through which poverty impacts neural
  processing of threat-related information in youth'
author: "David Weissman"
date: "7/6/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pscl)
library(MASS)
library(ggplot2)
library(patchwork)
library(lavaan)
library(boot)
library(mctest)
load("DepThreat.RData")
```

#Age 3 income (log transformed) and early adolescent mental health
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
summary(lm(CDI_TOT~SEX+S3AGE+logITN_age3,data=dtf))
summary(lm(SCARED_TOT~SEX+S3AGE+logITN_age3,data=dtf))
summary(zeroinfl(PTSD_SEV_COMBINED~SEX+S3AGE+logITN_age3,data=dtf))
```
#Age 3 income (log transformed) and adolescent adversity
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
summary(lm(FINAL_THREAT~SEX+S3AGE+logITN_age3,data=dtf))
summary(lm(FINAL_DEPRIVATION~SEX+S3AGE+logITN_age3,data=dtf))
```

#Deprivation and Threat and early adolescent mental health
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
summary(lm(CDI_TOT~FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
summary(lm(SCARED_TOT~FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
summary(zeroinfl(PTSD_SEV_COMBINED~FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
```

#multicollinearity check
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
imcdiag(lm(CDI_TOT~FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
imcdiag(lm(SCARED_TOT~FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
imcdiag(zeroinfl(PTSD_SEV_COMBINED~FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
```

#Mediation of the association between age 3 family income (log transformed) and Depression by Deprivation and Threat
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
DepMed <- function(x, id) {
  data <- x[id,]
  OutcomeModel <- coef(lm(CDI_TOT ~ FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3, data = data))
  OutcomeModelAlone <- coef(lm(CDI_TOT ~ logITN_age3, data = data))
  MedModel1 <- coef(lm(FINAL_THREAT ~ logITN_age3, data = data))
  MedModel2 <- coef(lm(FINAL_DEPRIVATION ~ logITN_age3, data = data))
  type1 <- unname(OutcomeModel["FINAL_THREAT"] * MedModel1["logITN_age3"])
  type2 <- unname(OutcomeModel["FINAL_DEPRIVATION"] * MedModel2["logITN_age3"])
  return(c(type1 = type1,type2=type2))
}
set.seed(123) 
boot.DepMed <- boot(dtf, statistic = DepMed, R = 10000)
boot.DepMed 
boot.ci(boot.DepMed, type = "bca", index = 1)
boot.ci(boot.DepMed, type = "bca", index = 2)
```

#Mediation of the association between age 3 family income (log transformed) and PTSD (zero and count) by Threat
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
PTMed <- function(x, id) {
  data <- x[id,]
  OutcomeModel <- coef(zeroinfl(PTSD_SEV_COMBINED ~ FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3, data = data))
  OutcomeModelAlone <- coef(zeroinfl(PTSD_SEV_COMBINED ~ logITN_age3, data = data))
  MedModel <- coef(lm(FINAL_THREAT ~ logITN_age3, data = data))
  type1 <- unname(OutcomeModel["count_FINAL_THREAT"] * MedModel["logITN_age3"])
  type2 <- unname(OutcomeModel["zero_FINAL_THREAT"] * MedModel["logITN_age3"])
  return(c(type1 = type1,type2=type2))
}
set.seed(123) 
boot.PTMed <- boot(dtf, statistic = PTMed, R = 10000)
boot.PTMed 
boot.ci(boot.PTMed, type = "bca", index = 1)
boot.ci(boot.PTMed, type = "bca", index = 2)
```

#Association between income, Deprivation, threat, and Amygdala ROIs (Fear vs. Calm)
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
summary(lm(lamyg.Fear_GT_Calm~SEX+S3AGE+logITN_age3,data=dtf))
summary(lm(lamyg.Fear_GT_Calm~FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
summary(lm(ramyg.Fear_GT_Calm~SEX+S3AGE+logITN_age3,data=dtf))
summary(lm(ramyg.Fear_GT_Calm~FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
```

#ROIs from whole brain analysis and Depression
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
summary(lm(CDI_TOT~Fear_GT_Calm.pcc+FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
summary(lm(CDI_TOT~Fear_GT_Calm.mpfc+FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
```
#multicollinearity check
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
imcdiag(lm(CDI_TOT~Fear_GT_Calm.pcc+FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
imcdiag(lm(CDI_TOT~Fear_GT_Calm.mpfc+FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
```
#ROIs from whole brain analysis and PTSD
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
summary(zeroinfl(PTSD_SEV_COMBINED~SEX+S3AGE+logITN_age3+FINAL_THREAT+FINAL_DEPRIVATION+Fear_GT_Calm.pcc,data=dtf))
summary(zeroinfl(PTSD_SEV_COMBINED~Fear_GT_Calm.mpfc+FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
```
#multicollinearity check
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
imcdiag(zeroinfl(PTSD_SEV_COMBINED~SEX+S3AGE+logITN_age3+FINAL_THREAT+FINAL_DEPRIVATION+Fear_GT_Calm.pcc,data=dtf))
imcdiag(zeroinfl(PTSD_SEV_COMBINED~Fear_GT_Calm.mpfc+FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3,data=dtf))
```

#Mediation of the association between age 3 family income (log transformed) and PTSD (count) by precuneus
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
PTpccITNMed <- function(x, id) {
  data <- x[id,]
  OutcomeModel <- coef(zeroinfl(PTSD_SEV_COMBINED ~ Fear_GT_Calm.pcc+FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3, data = data))
  OutcomeModelAlone <- coef(zeroinfl(PTSD_SEV_COMBINED ~ logITN_age3, data = data))
  MedModel <- coef(lm(Fear_GT_Calm.pcc ~ logITN_age3, data = data))
  type1 <- unname(OutcomeModel["count_Fear_GT_Calm.pcc"] * MedModel["logITN_age3"])
  return(type1 = type1)
}
set.seed(123) 
boot.PTpccITNMed <- boot(dtf, statistic = PTpccITNMed, R = 10000)
boot.PTpccITNMed 
boot.ci(boot.PTpccITNMed, type = "bca", index = 1)
```

#Mediation of the association between age 3 family income (log transformed) and PTSD (count) by dmPFC
```{r, warning=FALSE, message=FALSE, tidy=TRUE}
PTmpfcITNMed <- function(x, id) {
  data <- x[id,]
  OutcomeModel <- coef(zeroinfl(PTSD_SEV_COMBINED ~ Fear_GT_Calm.mpfc+FINAL_THREAT+FINAL_DEPRIVATION+SEX+S3AGE+logITN_age3, data = data))
  OutcomeModelAlone <- coef(zeroinfl(PTSD_SEV_COMBINED ~ logITN_age3, data = data))
  MedModel <- coef(lm(Fear_GT_Calm.mpfc ~ logITN_age3, data = data))
  type1 <- unname(OutcomeModel["count_Fear_GT_Calm.mpfc"] * MedModel["logITN_age3"])
  return(type1 = type1)
}
set.seed(123) 
boot.PTmpfcITNMed <- boot(dtf, statistic = PTmpfcITNMed, R = 10000)
boot.PTmpfcITNMed 
boot.ci(boot.PTmpfcITNMed, type = "bca", index = 1)
```